Validation of Visual Statistical Inference, with Application to Linear Models

### 2012-02-09 paper_jasa.tex
tweaking plots

\begin{figure}[hbt]
%\begin{figurehere}
   \centering
       \scalebox{0.65}{\includegraphics{test_category.pdf}}
       \caption{Lineup plot ($m=20$) for testing $H_0: \beta_k=0$. When the alternative hypothesis is true the observed plot should show a vertical displacement between box plots. Can you identify the observed plot?}
       \label{fig:test_category}
\end{figure}
%\end{figurehere}

@@

\begin{figure}[hbtp]
   \centering
       \scalebox{.45}{\includegraphics{power_expected.pdf}}
       \caption{Expected power of visual test  and the power of UMP test for sample size $n =100$ and $\sigma = 12$.}
       \label{fig:power_expected}
\end{figure}

>>>>

\begin{figure}[hbt]
%\begin{figurehere}
   \centering
       \scalebox{0.95}{\includegraphics{test_category.pdf}}
       \caption{Lineup plot ($m=20$) for testing $H_0: \beta_k=0$. When the alternative hypothesis is true the plot of the observed data should show a vertical displacement between box plots. Which plot has the biggest vertical displacement between the boxplots?}
       \label{fig:test_category}
\end{figure}
%\end{figurehere}

@@

\begin{figure}[hbtp]
   \centering
       \scalebox{.65}{\includegraphics{power_expected.pdf}}
       \caption{Expected power of visual test  and the power of UMP test for sample size $n =100$ and $\sigma = 12$.}
       \label{fig:power_expected}
\end{figure}
